\textbf{A Serious Game for Aiding the Screening of Dyslexia in Children and Young Adults}

### 2014-06-25 article.tex
Proof Introduction

\IEEEPARstart{T}{argeting} adolescents, this work examines whether the conventional screening
test for dyslexia could be replaced with a serious game. The game aims to use gameplay performance metrics of a player to predict wether they are likely to have dyslexia. The game also aims to screen individuals without explicitly highlighting the literacy and phonological deficits often associated with dyslexia, with the hope of 
producing an engaging experience for those with and without dyslexia. 
If the game is successful, it should vastly reduce the cost, personnel, and time taken to 
identify dyslexia through not requiring a specialist dyslexia teacher, or psychologist, to 
conduct a screening test \cite{bda, dast}. Hopefully the accessibility of the game, to 
teachers, parents, and students themselves, will result in more
young people being tested and receiving the specialist help they require.

The following examines current literature surrounding both dyslexia and games, to determine the breadth of current knowledge in both areas and show how combining the two fields could change what is state-of-the-art. This knowledge is then used to create a digital game built to screen for dyslexia. The created game is then evaluated through a user study.

>>>>

\IEEEPARstart{T}{argeting} adolescents and young adults, between the ages of eleven and twenty-five, this work examines whether the conventional screening test for dyslexia could be replaced with a serious game. 
The game aims to collect performance metrics about users and use them to predict whether they are likely to have dyslexia. 
The game also aims to screen individuals without explicitly highlighting the literacy and phonological deficits often associated with dyslexia, with the hope of producing an engaging experience for those with and without dyslexia. 
If the game is successful, it should vastly reduce the cost, personnel, and time taken to identify dyslexia through not requiring a specialist dyslexia teacher or psychologist to conduct a screening test \cite{bda, dast}. 
Hopefully the accessibility of the game, to teachers, parents, and students themselves, will result in more young people being tested and receiving the specialist help they require.

The remainder of this work examines the current literature surrounding both dyslexia and games, to determine the breadth of current knowledge in both areas and show how combining the two fields could change what is state-of-the-art. This knowledge is then used to create a digital game built to screen for dyslexia. The created game is then evaluated through a user study.
